\documentclass[11pt]{article}

\usepackage[letterpaper,
left=1.75in,
right=.75in,
top=0.5in,
bottom=0.5in]{geometry}

% Fonts:
\usepackage{ebgaramond}
\usepackage[scaled]{helvet}

\usepackage{enumitem}
%\usepackage{mathtools} % Better implementation of braces
\usepackage{abraces}
\usepackage{hyperref}  % For PDF link

\usepackage[activate={true,nocompatibility},
final,
protrusion=true,
expansion=true,
tracking=true,
kerning=true,
spacing=true,
factor=1100,
stretch=10,
shrink=10]{microtype}
\usepackage{titlesec}

\pagestyle{empty}
\setlength{\parindent}{0em}

\newcommand{\position}[2]{#1 \hfill #2}
\newcommand{\emphasized}[2]{\emphasis{#1} \medemph{#2}}
\newcommand{\heading}[1]{\section*{#1}}
\newcommand{\emphasis}[1]{\textbf{\textsf{#1}}}
\newcommand{\medemph}[1]{\textsf{#1}}
\newcommand{\link}[2]{\medemph{\hfill \small \href{#1}{#2}}}

% Make the sections go on the left
%\geometry{left=6cm,right=3cm} % 3cm for the sections
\titleformat{\section}[leftmargin]
{\sffamily\bfseries\filright}
{\thesection}
{1em}
{}
\titlespacing*{\section}
{3cm}
{2ex plus .2ex minus .2ex}
{1sp}% should be 0, but it must be positive

% Experience environment
\newenvironment{experience}{
	\begin{itemize}[leftmargin=*, topsep=0pt] % Aligns bullets to left margin, no spacing
		\setlength{\itemsep}{0pt} % Vertical space added after each item in the list.
		\setlength{\parskip}{0pt} % Horizontal space added at the beginning of each paragraph
		\setlength{\parsep}{10pt} % Vertical space added after each paragraph in the list.
	}{
	\end{itemize}
}

%\renewcommand{\labelitemi}{$\cdot$}
%\renewcommand{\labelitemii}{$\cdot$}
%\renewcommand{\familydefault}{\sfdefault}

\reversemarginpar

\begin{document}
	
\hspace{-3cm}\Large \textsf{\textbf{Philippe Chlenski}} \normalsize \hfill \medemph{312-545-3322}  $\vert$ 
$ \aoverbrace[L5UR]{
	\medemph{p@}\hspace{-.15em}\aunderbrace[l4Dr]{
		\medemph{chlenski.com}
	}_{\link{http://www.chlenski.com}{website}}
}^{\link{mailto:p@chlenski.com}{email}} $

\vfill

\heading{Education:}

\emphasized{Yale University,}{New Haven, CT} \hfill 2018
\begin{experience}
	\item BA with distinction in Mathematics \& Philosophy, \textit{cum laude}
	\item GPA: 3.85\\
\end{experience}

\emphasized{Deep Springs College,}{Deep Springs, CA} \hfill 2014
\begin{experience}
	\item AA in Liberal Arts
	\item GPA: 3.76
\end{experience}

\heading{Experience:}

\emphasized{Student Technology Collaborative,}{New Haven, CT}
\begin{experience}
	\item \position{Summer Conference Coordinator}{May 2017--Present}
	\begin{experience}
		\item Selective summer position for outstanding technicians, Summer 2017 and 2018.
		\item Manage access credentials and technical support for 4,000 campus visitors and 2,000 summer students. 
	\end{experience}
	\item \position{Hardware Specialist}{Oct 2017--May 2018}
	\begin{experience}
		\item Provided hardware support to roughly 13,000 students.
		\item Performed complex hardware repair on modern computer brands including Apple, Lenovo, and Dell.
		\item Trained, mentored, and evaluated other technicians for promotion to Hardware Specialist. 
	\end{experience}
	\item \position{Queue Coordinator}{Jan 2017--May 2018}
	\begin{experience}
		\item Managed a team of 4 technicians to provide technical support for over 900 graduate students.
	\end{experience}
	\item \position{Student Technician}{Dec 2015--May 2018}
	\begin{experience}
		\item Assisted students with technical issues in person or via ServiceNow. 
		\item Documented work performed and followed up with clients.\\
	\end{experience}
\end{experience}

\emphasized{Yale Sustainable Food Program,}{New Haven, CT}
\begin{experience}
	\item \position{Senior Adviser}{Sep 2016--May 2017}
	\begin{experience}
		\item Migrated organizational content to WordPress site with custom theme.
	\end{experience}
	\item \position{Lazarus Summer Intern}{May 2016--Sep 2016}
	\begin{experience}
		\item Planned and led volunteer programming on a one-acre educational farm. 
		\item Assisted in event planning for the MAD/Yale Leadership Summit. 
		\item Designed and performed independent computational research using R.\\
	\end{experience}
\end{experience}

\emphasized{Yale College Dean's Office,}{New Haven, CT}
\begin{experience}
	\item \position{Head Transfer Counselor}{May 2016--May 2017}
	\begin{experience}
		\item Managed and created guidelines for a team of 16 transfer counselors.
		\item Planned orientation events and created resources for posterity.
		\item Followed up on long-term transfer student integration.\\ 
	\end{experience}
\end{experience}

%\emphasized{The New Journal at Yale,}{New Haven, CT}
%\begin{experience}
%	\item \position{Web Developer}{Sep 2015--May 2017}
%	\begin{experience}
%		\item Implemented a custom, automated WordPress deployment of a website based on proofs from a graphic designer. 
%		\item Codified best practices for web, including fundraising protocols and web analytics.\\
%	\end{experience}
%\end{experience}

\emphasized{Northwestern University,}{Chicago, IL}
\begin{experience}
	\item \position{Web Development Intern}{Jun 2015--Aug 2015}
	\begin{experience}
		\item Created a searchable online tissue archive using PHP, MySQL, HTML/CSS, and jQuery.
	\end{experience}
	\item \position{Data Science Intern}{Jun 2013--Aug 2013}
	\begin{experience}
		\item Used R to analyze datasets pertaining to radiation oncology.
	\end{experience}
\end{experience}

\heading{Languages:} Russian, English, French.
%\heading{Technology:} Linux/Unix, FreeBSD, Adobe Creative Suite, Google Analytics, WordPress, Windows, MacOS, ServiceNow, Asterisk, Apple GSX, LaTeX.
\heading{Programming:} Python (including TensorFlow), R, Racket, PHP, MySQL, HTML/CSS, jQuery, bash.
\heading{Certifications:} Apple ACST, ACMT, ACiT; Lenovo Service Authorization; Dell Service Authorization.



\end{document}